This is a collection of use case descriptions (one per use case).
Think carefully about how to group these descriptions in the document.
You can use the template style provided to format your descriptions:

ADDED THIS TO CHECK


\begin{UseCaseTemplate}
\UseCaseLabel{Student Logs into system}
\UseCaseDescription{A student from the University of Glasgow
  interested in applying for a summer placement/internship gains
  access to the system by logging in.}
\UseCaseRationale{A student should be able to log into the
  system. This gives the system added protection and privacy to those
  who should not have access to the system.}
\UseCasePriority{High}
\UseCaseStatus{Uncomplete}
\UseCaseActors{Student}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Successful log in, Unsuccessful log in.}
\UseCaseRisks{Unable to link with GUID log in which may mean students
  have to enrol for service. }
\UseCaseUserInterface{Log in screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{Notification of new placement}
\UseCaseDescription{When a new placement is accepted by the course
  coordinator, all student in Level 3 CS should be notified of it by 
  email.}
\UseCaseRationale{A useful feature to aid CS students in their search
  for a placement}
\UseCasePriority{Medium}
\UseCaseStatus{Uncomplete}
\UseCaseActors{Student, Course Coordinator}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{Notification Sent}
\UseCaseRisks{Handeling the response from an email being sent to a 
  non-existent email address or to an email address that causes a 
  bounceback/send fail message. A student neglecting to view emails
  sent by the service due to mass emails sent when many advertisements
  go live on one day.}
\UseCaseUserInterface{Course Coordinator Advert View Screen.}
\end{UseCaseTemplate}

\begin{UseCaseTemplate}
\UseCaseLabel{}
\UseCaseDescription{}
\UseCaseRationale{}
\UseCasePriority{}
\UseCaseStatus{}
\UseCaseActors{}
\UseCaseExtensions{}
\UseCaseIncludes{}
\UseCaseConditions{}
\UseCaseNonFunctionalRequirements{}
\UseCaseScenarios{}
\UseCaseRisks{}
\UseCaseUserInterface{}
\end{UseCaseTemplate}
